---
title: "Analysis with belonging to minority and being in a relationship added as covariates"
output: 
  html_document: 
    toc: yes
    keep_md: yes
    toc_depth: 5
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Preparations

## Packages

```{r message=FALSE, warning=FALSE}

library(mclogit)
library(emmeans)
library(dplyr)
library(rio)
library(memisc)
library(psych)
library(ggplot2)
library(ggpubr)
library(lme4)
library(MetBrewer)
source("../custom_functions.R")
```
## Dataset

```{r}
fdat<-import("../../data/processed/fdat.xlsx")
```

## Data transformations

The reference levels for factorial variables need to be redefined, .xlsx format does not understand factor formats.

### Income

```{r}
fdat$income.f<-case_when(
  is.na(fdat$income) ~ "missing",
  TRUE ~ fdat$income
)

#define reference level (top quintile)
table(fdat$income.f,useNA="always")
fdat$income.fr = relevel(as.factor(fdat$income.f), ref="quint.5")
table(fdat$income.fr,useNA="always")
```

### Education

```{r}
table(fdat$edu,useNA="always")
fdat$edu.f<-relevel(as.factor(fdat$edu),ref="7. MA")
table(fdat$edu.f,useNA="always")
```

### DV

```{r}
table(fdat$DV,useNA="always")
fdat$DV.f<-relevel(as.factor(fdat$DV),ref="NN")
table(fdat$DV.f,useNA="always")
```

### Strain on health and political orientation

Calculate country means for centering

```{r}
# Calculate country means for centering

cntry.means<-fdat %>%
  group_by(cntry) %>%
  summarise(strain.on.health.cntry.mean=
              mean(strain.on.health,na.rm=T),
            lrgen.cntry.mean=
              mean(lrgen,na.rm=T),
            lrecon.cntry.mean=
              mean(lrecon,na.rm=T),
            galtan.cntry.mean=
              mean(galtan,na.rm=T),
            antielite_salience.cntry.mean=
              mean(antielite_salience,na.rm=T),
            corrupt_salience.cntry.mean=
              mean(corrupt_salience,na.rm=T))

#combine data frames

fdat<-left_join(
  x=fdat,
  y=cntry.means,
  by="cntry"
)

#country-mean center strain on health

fdat$strain.on.health.c<-
  fdat$strain.on.health-fdat$strain.on.health.cntry.mean

#country-mean center political orientation

fdat$lrgen.c<-
  fdat$lrgen-fdat$lrgen.cntry.mean
fdat$lrecon.c<-
  fdat$lrecon-fdat$lrecon.cntry.mean
fdat$galtan.c<-
  fdat$galtan-fdat$galtan.cntry.mean
fdat$antielite_salience.c<-
  fdat$antielite_salience-fdat$antielite_salience.cntry.mean
fdat$corrupt_salience.c<-
  fdat$corrupt_salience-fdat$corrupt_salience.cntry.mean

#scale with CHES grand SD
fdat$lrgen.z<-
  fdat$lrgen.c/fdat$lrgen.scaling
fdat$lrecon.z<-
  fdat$lrecon.c/fdat$lrecon.scaling
fdat$galtan.z<-
  fdat$galtan.c/fdat$galtan.scaling
fdat$antielite_salience.z<-
  fdat$antielite_salience.c/fdat$antielite_salience.scaling
fdat$corrupt_salience.z<-
  fdat$corrupt_salience.c/fdat$corrupt_salience.scaling
```

## Exclude missing variable

```{r}

fdat<-fdat %>%
  filter(cntry!="IL" & cntry!="EE") %>%
  filter(!is.na(cntry) & 
         !is.na(gndr.c) &
         !is.na(age10.c) &
         !is.na(income.fr) &
           !is.na(edu.f) &
           !is.na(strain.on.health.c) &
           !is.na(DV) &
           !is.na(lrgen.z) &
           !is.na(lrecon.z) &
           !is.na(galtan.z) &
           !is.na(antielite_salience.z) &
           !is.na(corrupt_salience.z))

```

## Construct anweight variable for weighting

```{r}
fdat$anweight=fdat$pspwght*fdat$pweight
```

# Descriptive analysis

## Check the presence of all DV-groups across countries

```{r}
table(fdat$cntry,fdat$DV.f)
round(100*prop.table(table(fdat$cntry,fdat$DV.f),
                     margin = 1),1)
```


# Analysis

## Empty model

```{r}
mod0<-mblogit(DV.f~1,
              random= ~1|cntry,
              estimator="ML",
              data=fdat,weights=anweight)

mod0
summary(mod0)
mtable(mod0,show.baselevel = T)
```

## Model with covariates

```{r}
mod1<-
  mblogit(DV.f~gndr.c+age10.c+income.fr+edu.f+blgetmg.c+mstatus.c+
            strain.on.health.c,
              random= ~1|cntry,
              estimator="ML",
              data=fdat,weights=anweight)

summary(mod1)
mod1
mtable(mod1,show.baselevel = T)
```

### Strain on health main effects

```{r}

mod1.strain.trends<-
  emtrends(mod1,~1|DV.f,
           var="strain.on.health.c",
           infer=T,mode="latent",
           at=list(gndr.c=0,age10.c=0))

#effects for each DV-category
(mod1.strain.eff<-
  contrast(mod1.strain.trends,simple="DV.f",
         adjust="none","eff",infer=c(T,T)))

#save to file
export(data.frame(mod1.strain.eff),
       "../../results/Added_covariates/mod1.strain.eff.MN.xlsx",
       overwrite=T)

#Use of conventional medicine

(mod1.strain.eff.CM<-
  contrast(mod1.strain.trends,
           method = list("Conv - No conv" = contrast.weights.total(effects=mod1.strain.eff,
          signs=c(-2,-2,2,2))),
           simple="DV.f",
           infer=c(T,T)))


(mod1.strain.eff.CAM<-
    contrast(mod1.strain.trends,
         method = list("CAM - No CAM" = contrast.weights.total(effects=mod1.strain.eff,
                 signs=c(-2,2,2,-2))),
         simple="DV.f",
           infer=c(T,T)))

# save to file
export(data.frame(rbind(mod1.strain.eff.CM,
      mod1.strain.eff.CAM,adjust="none")),
      "../../results/Added_covariates/mod1.strain.eff.COMB.xlsx")

```

### gender main effects

```{r}

mod1.gndr.trends<-
  emtrends(mod1,~1|DV.f,
           var="gndr.c",
           infer=T,mode="latent",
           at=list(strain.on.health.c=0,age10.c=0))

#effects for each DV-category
(mod1.gndr.eff<-
  contrast(mod1.gndr.trends,simple="DV.f",
         adjust="none","eff",infer=c(T,T)))

#save to file
export(data.frame(mod1.gndr.eff),
       "../../results/Added_covariates/mod1.gndr.eff.MN.xlsx",
       overwrite=T)

#Use of conventional medicine

(mod1.gndr.eff.CM<-
  contrast(mod1.gndr.trends,
           method = list("Conv - No conv" = contrast.weights.total(effects=mod1.gndr.eff,
          signs=c(-2,-2,2,2))),
           simple="DV.f",
           infer=c(T,T)))


(mod1.gndr.eff.CAM<-
    contrast(mod1.gndr.trends,
         method = list("CAM - No CAM" = contrast.weights.total(effects=mod1.gndr.eff,
                 signs=c(-2,2,2,-2))),
         simple="DV.f",
           infer=c(T,T)))

# save to file
export(data.frame(rbind(mod1.gndr.eff.CM,
      mod1.gndr.eff.CAM,adjust="none")),
      "../../results/Added_covariates/mod1.gndr.eff.COMB.xlsx")

```


### age main effects

```{r}

mod1.age10.trends<-
  emtrends(mod1,~1|DV.f,
           var="age10.c",
           infer=T,mode="latent",
           at=list(strain.on.health.c=0,gndr.c=0))

#effects for each DV-category
(mod1.age10.eff<-
  contrast(mod1.age10.trends,simple="DV.f",
         adjust="none","eff",infer=c(T,T)))

#save to file
export(data.frame(mod1.age10.eff),
       "../../results/Added_covariates/mod1.age10.eff.MN.xlsx",
       overwrite=T)

#Use of conventional medicine

(mod1.age10.eff.CM<-
  contrast(mod1.age10.trends,
           method = list("Conv - No conv" = contrast.weights.total(effects=mod1.age10.eff,
          signs=c(-2,-2,2,2))),
           simple="DV.f",
           infer=c(T,T)))


(mod1.age10.eff.CAM<-
    contrast(mod1.age10.trends,
         method = list("CAM - No CAM" = contrast.weights.total(effects=mod1.age10.eff,
                 signs=c(-2,2,2,-2))),
         simple="DV.f",
           infer=c(T,T)))

# save to file
export(data.frame(rbind(mod1.age10.eff.CM,
      mod1.age10.eff.CAM,adjust="none")),
      "../../results/Added_covariates/mod1.age10.eff.COMB.xlsx")

```


### education main effects

```{r}
# first take probabilities for all categories
mod1.edu.f.trends<-emmeans(mod1,by="DV.f",
        specs="edu.f",
        infer=T,mode="prob",
        at=list(strain.on.health.c=0,gndr.c=0,age10.c=0))

mod1.edu.f.trends


export(data.frame(mod1.edu.f.trends),
       "../../results/Added_covariates/mod1.edu.f.eff.MN.xlsx",
       overwrite=T)


#effects for each DV-category
(mod1.edu.f.eff<-
    contrast(mod1.edu.f.trends,#simple="edu.f",
             adjust="none","eff",infer=c(T,T)))

#save to file
export(data.frame(mod1.edu.f.eff),
       "../../results/Added_covariates/mod1.edu.f.eff.MN.xlsx",
       overwrite=T)

# No Conv versus Conv

(mod1.edu.f.eff_DV<-
    contrast(mod1.edu.f.trends,simple="DV.f",
             adjust="none","eff",infer=c(T,T)))


(mod1.edu.f.eff.CM<-
    contrast(mod1.edu.f.trends,
             method = 
               list("Conv - No conv" = c(0,0,1,1)),
             simple="DV.f",
             infer=c(T,T)))

(mod1.edu.f.eff.CM_comp<-
  contrast(mod1.edu.f.eff.CM,
         simple="edu.f",method="eff",
         infer=c(T,T),adjust="none"))

# No CAM versus CAM


(mod1.edu.f.eff.CAM<-
    contrast(mod1.edu.f.trends,
             method = 
               list("CAM - No CAM" = c(0,1,1,0)),
             simple="DV.f",
             infer=c(T,T)))

(mod1.edu.f.eff.CAM_comp<-
    contrast(mod1.edu.f.eff.CAM,
             simple="edu.f",method="eff",
             infer=c(T,T),adjust="none"))


# save to file
export(data.frame(rbind(mod1.edu.f.eff.CM_comp,
                        mod1.edu.f.eff.CAM_comp,adjust="none")),
       "../../results/Added_covariates/mod1.edu.f.eff.COMB_comp.xlsx",overwrite=T)

# save to file
export(data.frame(rbind(mod1.edu.f.eff.CM,
                        mod1.edu.f.eff.CAM,adjust="none")),
       "../../results/Added_covariates/mod1.edu.f.eff.COMB.xlsx",overwrite=T)
```


### income main effects

```{r}
# first take probabilities for all categories
mod1.income.fr.trends<-emmeans(mod1,by="DV.f",
        specs="income.fr",
        infer=T,mode="prob",
        at=list(strain.on.health.c=0,gndr.c=0,age10.c=0))

mod1.income.fr.trends


export(data.frame(mod1.income.fr.trends),
       "../../results/Added_covariates/mod1.income.fr.eff.MN.xlsx",
       overwrite=T)


#effects for each DV-category
(mod1.income.fr.eff<-
    contrast(mod1.income.fr.trends,#simple="income.fr",
             adjust="none","eff",infer=c(T,T)))

#save to file
export(data.frame(mod1.income.fr.eff),
       "../../results/Added_covariates/mod1.income.fr.eff.MN.xlsx",
       overwrite=T)

# No Conv versus Conv

(mod1.income.fr.eff_DV<-
    contrast(mod1.income.fr.trends,simple="DV.f",
             adjust="none","eff",infer=c(T,T)))


(mod1.income.fr.eff.CM<-
    contrast(mod1.income.fr.trends,
             method = 
               list("Conv - No conv" = c(0,0,1,1)),
             simple="DV.f",
             infer=c(T,T)))

(mod1.income.fr.eff.CM_comp<-
  contrast(mod1.income.fr.eff.CM,
         simple="income.fr",method="eff",
         infer=c(T,T),adjust="none"))

# No CAM versus CAM


(mod1.income.fr.eff.CAM<-
    contrast(mod1.income.fr.trends,
             method = 
               list("CAM - No CAM" = c(0,1,1,0)),
             simple="DV.f",
             infer=c(T,T)))

(mod1.income.fr.eff.CAM_comp<-
    contrast(mod1.income.fr.eff.CAM,
             simple="income.fr",method="eff",
             infer=c(T,T),adjust="none"))


# save to file
export(data.frame(rbind(mod1.income.fr.eff.CM_comp,
                        mod1.income.fr.eff.CAM_comp,adjust="none")),
       "../../results/Added_covariates/mod1.income.fr.eff.COMB_comp.xlsx",overwrite=T)

# save to file
export(data.frame(rbind(mod1.income.fr.eff.CM,
                        mod1.income.fr.eff.CAM,adjust="none")),
       "../../results/Added_covariates/mod1.income.fr.eff.COMB.xlsx",overwrite=T)
```

## Model for lrgen

```{r}
mod2.lrgen<-
  mblogit(DV.f~gndr.c+age10.c+income.fr+edu.f+blgetmg.c+mstatus.c+
            strain.on.health.c+
            lrgen.z,
                    random= ~1|cntry,
                    estimator="ML",
                    control = mmclogit.control(maxit = 250, trace=TRUE),
                    data=fdat,weights=anweight)

# general model comparison

anova(mod1,mod2.lrgen,test="Chisq")

# Is lrgen associated with using conventional medicine?
ref_grid(mod2.lrgen)
mod2.lrgen.trends<-
  emtrends(mod2.lrgen,~1|DV.f,
           var="lrgen.z",infer=c(T,T),mode="latent",
           at=list(gndr.c=0,age10.c=0,
                   strain.on.health.c=0))

#effects for each DV-category
(mod2.lrgen.eff<-
  contrast(mod2.lrgen.trends,simple="DV.f",
         adjust="none","eff", infer=c(T,T)))

#save to file
export(data.frame(mod2.lrgen.eff),
       "../../results/Added_covariates/mod2.lrgen.eff.MN.xlsx",
       overwrite=T)

#Use of conventional medicine

(mod2.lrgen.eff.CM<-
    contrast(mod2.lrgen.trends,
         method = list("Conv - No conv" = contrast.weights.total(effects=mod2.lrgen.eff,
                 signs=c(-2,-2,2,2))),
         simple="DV.f", infer=c(T,T)))

#Use of CAM

(mod2.lrgen.eff.CAM<-
    contrast(mod2.lrgen.trends,
         method = list("CAM - No CAM" = contrast.weights.total(effects=mod2.lrgen.eff,
                 signs=c(-2,2,2,-2))),
         simple="DV.f", infer=c(T,T)))


# save to file
export(data.frame(rbind(
  mod2.lrgen.eff.CM,
  mod2.lrgen.eff.CAM,adjust="none")),
  "../../results/Added_covariates/mod2.lrgen.eff.COMB.xlsx")
```

## Model for lrecon

```{r}
mod2.lrecon<-
  mblogit(DV.f~gndr.c+age10.c+income.fr+edu.f+blgetmg.c+mstatus.c+
            strain.on.health.c+
            lrecon.z,
                    random= ~1|cntry,
                    estimator="ML",
                    control = mmclogit.control(maxit = 250, trace=TRUE),
                    data=fdat,weights=anweight)

# general model comparison

anova(mod1,mod2.lrecon,test="Chisq")

# Is lrecon associated with using conventional medicine?
ref_grid(mod2.lrecon)
mod2.lrecon.trends<-
  emtrends(mod2.lrecon,~1|DV.f,
           var="lrecon.z",infer=c(T,T),mode="latent",
           at=list(gndr.c=0,age10.c=0,
                   strain.on.health.c=0))

#effects for each DV-category
(mod2.lrecon.eff<-
  contrast(mod2.lrecon.trends,simple="DV.f",
         adjust="none","eff", infer=c(T,T)))

#save to file
export(data.frame(mod2.lrecon.eff),
       "../../results/Added_covariates/mod2.lrecon.eff.MN.xlsx",
       overwrite=T)

#Use of conventional medicine

(mod2.lrecon.eff.CM<-
    contrast(mod2.lrecon.trends,
         method = list("Conv - No conv" = contrast.weights.total(effects=mod2.lrecon.eff,
                 signs=c(-2,-2,2,2))),
         simple="DV.f", infer=c(T,T)))

#Use of CAM

(mod2.lrecon.eff.CAM<-
    contrast(mod2.lrecon.trends,
         method = list("CAM - No CAM" = contrast.weights.total(effects=mod2.lrecon.eff,
                 signs=c(-2,2,2,-2))),
         simple="DV.f", infer=c(T,T)))


# save to file
export(data.frame(rbind(
  mod2.lrecon.eff.CM,
  mod2.lrecon.eff.CAM,adjust="none")),
  "../../results/Added_covariates/mod2.lrecon.eff.COMB.xlsx")
```

## Model for galtan

```{r}
mod2.galtan<-
  mblogit(DV.f~gndr.c+age10.c+income.fr+edu.f+blgetmg.c+mstatus.c+
            strain.on.health.c+
            galtan.z,
                    random= ~1|cntry,
                    estimator="ML",
                    control = mmclogit.control(maxit = 250, trace=TRUE),
                    data=fdat,weights=anweight)

# general model comparison

anova(mod1,mod2.galtan,test="Chisq")

# Is galtan associated with using conventional medicine?
ref_grid(mod2.galtan)
mod2.galtan.trends<-
  emtrends(mod2.galtan,~1|DV.f,
           var="galtan.z",infer=c(T,T),mode="latent",
           at=list(gndr.c=0,age10.c=0,
                   strain.on.health.c=0))

#effects for each DV-category
(mod2.galtan.eff<-
  contrast(mod2.galtan.trends,simple="DV.f",
         adjust="none","eff", infer=c(T,T)))

#save to file
export(data.frame(mod2.galtan.eff),
       "../../results/Added_covariates/mod2.galtan.eff.MN.xlsx",
       overwrite=T)

#Use of conventional medicine

(mod2.galtan.eff.CM<-
    contrast(mod2.galtan.trends,
         method = list("Conv - No conv" = contrast.weights.total(effects=mod2.galtan.eff,
                 signs=c(-2,-2,2,2))),
         simple="DV.f", infer=c(T,T)))

#Use of CAM

(mod2.galtan.eff.CAM<-
    contrast(mod2.galtan.trends,
         method = list("CAM - No CAM" = contrast.weights.total(effects=mod2.galtan.eff,
                 signs=c(-2,2,2,-2))),
         simple="DV.f", infer=c(T,T)))


# save to file
export(data.frame(rbind(
  mod2.galtan.eff.CM,
  mod2.galtan.eff.CAM,adjust="none")),
  "../../results/Added_covariates/mod2.galtan.eff.COMB.xlsx")
```

### Contrast between CAM-only and CAM-and-conv against no-CAM

```{r}

pairs(mod2.galtan.eff,adjust="none",infer=c(T,T))

#save to file

export(data.frame(pairs(mod2.galtan.eff,
                        adjust="none",
                        infer=c(T,T))),
  "../../results/Added_covariates/mod2.galtan.eff.CAM.contrast.xlsx")

```

## Model for antielite_salience

```{r}
mod2.antielite_salience<-
  mblogit(DV.f~gndr.c+age10.c+income.fr+edu.f+blgetmg.c+mstatus.c+
            strain.on.health.c+
            antielite_salience.z,
                    random= ~1|cntry,
                    estimator="ML",
                    control = mmclogit.control(maxit = 250, trace=TRUE),
                    data=fdat,weights=anweight)

# general model comparison

anova(mod1,mod2.antielite_salience,test="Chisq")

# Is antielite_salience associated with using conventional medicine?
ref_grid(mod2.antielite_salience)
mod2.antielite_salience.trends<-
  emtrends(mod2.antielite_salience,~1|DV.f,
           var="antielite_salience.z",infer=c(T,T),mode="latent",
           at=list(gndr.c=0,age10.c=0,
                   strain.on.health.c=0))

#effects for each DV-category
(mod2.antielite_salience.eff<-
  contrast(mod2.antielite_salience.trends,simple="DV.f",
         adjust="none","eff", infer=c(T,T)))

#save to file
export(data.frame(mod2.antielite_salience.eff),
       "../../results/Added_covariates/mod2.antielite_salience.eff.MN.xlsx",
       overwrite=T)

#Use of conventional medicine

(mod2.antielite_salience.eff.CM<-
    contrast(mod2.antielite_salience.trends,
         method = list("Conv - No conv" = contrast.weights.total(effects=mod2.antielite_salience.eff,
                 signs=c(-2,-2,2,2))),
         simple="DV.f", infer=c(T,T)))

#Use of CAM

(mod2.antielite_salience.eff.CAM<-
    contrast(mod2.antielite_salience.trends,
         method = list("CAM - No CAM" = contrast.weights.total(effects=mod2.antielite_salience.eff,
                 signs=c(-2,2,2,-2))),
         simple="DV.f", infer=c(T,T)))


# save to file
export(data.frame(rbind(
  mod2.antielite_salience.eff.CM,
  mod2.antielite_salience.eff.CAM,adjust="none")),
  "../../results/Added_covariates/mod2.antielite_salience.eff.COMB.xlsx")
```

## Model for corrupt_salience

```{r}
mod2.corrupt_salience<-
  mblogit(DV.f~gndr.c+age10.c+income.fr+edu.f+blgetmg.c+mstatus.c+
            strain.on.health.c+
            corrupt_salience.z,
                    random= ~1|cntry,
                    estimator="ML",
                    control = mmclogit.control(maxit = 250, trace=TRUE),
                    data=fdat,weights=anweight)

# general model comparison

anova(mod1,mod2.corrupt_salience,test="Chisq")

# Is corrupt_salience associated with using conventional medicine?
ref_grid(mod2.corrupt_salience)
mod2.corrupt_salience.trends<-
  emtrends(mod2.corrupt_salience,~1|DV.f,
           var="corrupt_salience.z",infer=c(T,T),mode="latent",
           at=list(gndr.c=0,age10.c=0,
                   strain.on.health.c=0))

#effects for each DV-category
(mod2.corrupt_salience.eff<-
  contrast(mod2.corrupt_salience.trends,simple="DV.f",
         adjust="none","eff", infer=c(T,T)))

#save to file
export(data.frame(mod2.corrupt_salience.eff),
       "../../results/Added_covariates/mod2.corrupt_salience.eff.MN.xlsx",
       overwrite=T)

#Use of conventional medicine

(mod2.corrupt_salience.eff.CM<-
    contrast(mod2.corrupt_salience.trends,
         method = list("Conv - No conv" = contrast.weights.total(effects=mod2.corrupt_salience.eff,
                 signs=c(-2,-2,2,2))),
         simple="DV.f", infer=c(T,T)))

#Use of CAM

(mod2.corrupt_salience.eff.CAM<-
    contrast(mod2.corrupt_salience.trends,
         method = list("CAM - No CAM" = contrast.weights.total(effects=mod2.corrupt_salience.eff,
                 signs=c(-2,2,2,-2))),
         simple="DV.f", infer=c(T,T)))


# save to file
export(data.frame(rbind(
  mod2.corrupt_salience.eff.CM,
  mod2.corrupt_salience.eff.CAM,adjust="none")),
  "../../results/Added_covariates/mod2.corrupt_salience.eff.COMB.xlsx")
```


### Contrast between CAM-only and CAM-and-conv against no-CAM

```{r}

pairs(mod2.corrupt_salience.eff,
      adjust="none",infer=c(T,T))

#save to file

export(data.frame(pairs(mod2.corrupt_salience.eff,
                        adjust="none",
                        infer=c(T,T))),
  "../../results/Added_covariates/mod2.corrupt_salience.eff.CAM.contrast.xlsx")
```

# Interactions by strain on health

## Model for lrgen

```{r}
mod3.lrgen<-
  mblogit(DV.f~gndr.c+age10.c+income.fr+
            edu.f+blgetmg.c+mstatus.c+strain.on.health.c+lrgen.z+
            strain.on.health.c:lrgen.z,
          random= ~1|cntry,
          estimator="ML",
          control = 
            mmclogit.control(maxit = 250,
                             trace=TRUE),
          data=fdat,weights=anweight)

anova(mod2.lrgen,mod3.lrgen,test="Chisq")

#Alternative model with manually defined interaction
fdat$lrgen.zXstrain.on.health.c<-fdat$lrgen.z*fdat$strain.on.health.c

mod3.lrgen.alt<-
  mblogit(DV.f~gndr.c+age10.c+income.fr+
            edu.f+blgetmg.c+mstatus.c+strain.on.health.c+lrgen.z+
            lrgen.zXstrain.on.health.c,
          random= ~1|cntry,
          estimator="ML",
          control = 
            mmclogit.control(maxit = 250,
                             trace=TRUE),
          data=fdat,weights=anweight)


mod3.lrgen.alt.trends<-
  emtrends(mod3.lrgen.alt,~1|DV.f,
           var="lrgen.zXstrain.on.health.c",
           infer=c(T,T),mode="latent",
           at=list(gndr.c=0,age10.c=0))

#effects for each DV-category
(mod3.lrgen.alt.eff<-
  contrast(mod3.lrgen.alt.trends,simple="DV.f",
         adjust="none","eff",infer=c(T,T)))

#save to file
export(data.frame(mod3.lrgen.alt.eff),
       "../../results/Added_covariates/mod3.lrgenBYhealth.eff.MN.xlsx",
       overwrite=T)

#Use of conventional medicine

(mod3.lrgen.eff.CM<-contrast(mod3.lrgen.alt.trends,
         method = list("Conv - No conv" = contrast.weights.total(effects=mod3.lrgen.alt.eff,
                 signs=c(-2,-2,2,2))),
         simple="DV.f", infer=c(T,T)))

#Use of CAM

#weighted across all effects

(mod3.lrgen.eff.CAM<-contrast(mod3.lrgen.alt.trends,
         method = list("CAM - No CAM" = contrast.weights.total(effects=mod3.lrgen.alt.eff,
                 signs=c(-2,2,2,-2))),
         simple="DV.f", infer=c(T,T)))

# save to file
export(data.frame(rbind(
  mod3.lrgen.eff.CM,
  mod3.lrgen.eff.CAM,adjust="none")),
  "../../results/Added_covariates/mod3.lrgenBYhealth.eff.COMB.xlsx")


```


## Model for lrecon

```{r}
mod3.lrecon<-
  mblogit(DV.f~gndr.c+age10.c+income.fr+
            edu.f+blgetmg.c+mstatus.c+strain.on.health.c+lrecon.z+
            strain.on.health.c:lrecon.z,
          random= ~1|cntry,
          estimator="ML",
          control = 
            mmclogit.control(maxit = 250,
                             epsilon=0.0001,
                             trace=TRUE),
          data=fdat,weights=anweight)

anova(mod2.lrecon,mod3.lrecon,test="Chisq")

#Alternative model with manually defined interaction
fdat$lrecon.zXstrain.on.health.c<-fdat$lrecon.z*fdat$strain.on.health.c

mod3.lrecon.alt<-
  mblogit(DV.f~gndr.c+age10.c+income.fr+
            edu.f+blgetmg.c+mstatus.c+strain.on.health.c+lrecon.z+
            lrecon.zXstrain.on.health.c,
          random= ~1|cntry,
          estimator="ML",
          control = 
            mmclogit.control(maxit = 250,
                             epsilon=0.0001,
                             trace=TRUE),
          data=fdat,weights=anweight)


mod3.lrecon.alt.trends<-
  emtrends(mod3.lrecon.alt,~1|DV.f,
           var="lrecon.zXstrain.on.health.c",
           infer=c(T,T),mode="latent",
           at=list(gndr.c=0,age10.c=0))

#effects for each DV-category
(mod3.lrecon.alt.eff<-
  contrast(mod3.lrecon.alt.trends,simple="DV.f",
         adjust="none","eff",infer=c(T,T)))

#save to file
export(data.frame(mod3.lrecon.alt.eff),
       "../../results/Added_covariates/mod3.lreconBYhealth.eff.MN.xlsx",
       overwrite=T)

#Use of conventional medicine

(mod3.lrecon.eff.CM<-contrast(mod3.lrecon.alt.trends,
         method = list("Conv - No conv" = contrast.weights.total(effects=mod3.lrecon.alt.eff,
                 signs=c(-2,-2,2,2))),
         simple="DV.f", infer=c(T,T)))

#Use of CAM

#weighted across all effects

(mod3.lrecon.eff.CAM<-contrast(mod3.lrecon.alt.trends,
         method = list("CAM - No CAM" = contrast.weights.total(effects=mod3.lrecon.alt.eff,
                 signs=c(-2,2,2,-2))),
         simple="DV.f", infer=c(T,T)))

# save to file
export(data.frame(rbind(
  mod3.lrecon.eff.CM,
  mod3.lrecon.eff.CAM,adjust="none")),
  "../../results/Added_covariates/mod3.lreconBYhealth.eff.COMB.xlsx")
```


## Model for galtan

(Here it was necessary to change the epsilon convergence criterion 1e-04 instead of 1e-08)

```{r}
mod3.galtan<-
  mblogit(DV.f~gndr.c+age10.c+income.fr+
            edu.f+blgetmg.c+mstatus.c+strain.on.health.c+galtan.z+
            strain.on.health.c:galtan.z,
          random= ~1|cntry,
          estimator="ML",
          control = 
            mmclogit.control(maxit = 250,
                             epsilon=0.0001,
                             trace=TRUE),
          data=fdat,weights=anweight)



anova(mod2.galtan,mod3.galtan,test="Chisq")

#Alternative model with manually defined interaction
fdat$galtan.zXstrain.on.health.c<-fdat$galtan.z*fdat$strain.on.health.c

mod3.galtan.alt<-
  mblogit(DV.f~gndr.c+age10.c+income.fr+
            edu.f+blgetmg.c+mstatus.c+strain.on.health.c+galtan.z+
            galtan.zXstrain.on.health.c,
          random= ~1|cntry,
          estimator="ML",
          control = 
            mmclogit.control(maxit = 250,
                             trace=TRUE,
                             epsilon=0.0001),
          data=fdat,weights=anweight)


mod3.galtan.alt.trends<-
  emtrends(mod3.galtan.alt,~1|DV.f,
           var="galtan.zXstrain.on.health.c",
           infer=c(T,T),mode="latent",
           at=list(gndr.c=0,age10.c=0))

#effects for each DV-category
(mod3.galtan.alt.eff<-
  contrast(mod3.galtan.alt.trends,simple="DV.f",
         adjust="none","eff",infer=c(T,T)))

#save to file
export(data.frame(mod3.galtan.alt.eff),
       "../../results/Added_covariates/mod3.galtanBYhealth.eff.MN.xlsx",
       overwrite=T)

#Use of conventional medicine

(mod3.galtan.eff.CM<-contrast(mod3.galtan.alt.trends,
         method = list("Conv - No conv" = contrast.weights.total(effects=mod3.galtan.alt.eff,
                 signs=c(-2,-2,2,2))),
         simple="DV.f", infer=c(T,T)))

#Use of CAM

#weighted across all effects

(mod3.galtan.eff.CAM<-contrast(mod3.galtan.alt.trends,
         method = list("CAM - No CAM" = contrast.weights.total(effects=mod3.galtan.alt.eff,
                 signs=c(-2,2,2,-2))),
         simple="DV.f", infer=c(T,T)))

# save to file
export(data.frame(rbind(
  mod3.galtan.eff.CM,
  mod3.galtan.eff.CAM,adjust="none")),
  "../../results/Added_covariates/mod3.galtanBYhealth.eff.COMB.xlsx")
```



## Model for antielite_salience

```{r}
mod3.antielite_salience<-
  mblogit(DV.f~gndr.c+age10.c+income.fr+
            edu.f+blgetmg.c+mstatus.c+strain.on.health.c+antielite_salience.z+
            strain.on.health.c:antielite_salience.z,
          random= ~1|cntry,
          estimator="ML",
          control = 
            mmclogit.control(maxit = 250,
                             trace=TRUE),
          data=fdat,weights=anweight)

anova(mod2.antielite_salience,
      mod3.antielite_salience,test="Chisq")

#Alternative model with manually defined interaction
fdat$antielite_salience.zXstrain.on.health.c<-fdat$antielite_salience.z*fdat$strain.on.health.c

mod3.antielite_salience.alt<-
  mblogit(DV.f~gndr.c+age10.c+income.fr+
            edu.f+blgetmg.c+mstatus.c+strain.on.health.c+antielite_salience.z+
            antielite_salience.zXstrain.on.health.c,
          random= ~1|cntry,
          estimator="ML",
          control = 
            mmclogit.control(maxit = 250,
                             trace=TRUE),
          data=fdat,weights=anweight)


mod3.antielite_salience.alt.trends<-
  emtrends(mod3.antielite_salience.alt,~1|DV.f,
           var="antielite_salience.zXstrain.on.health.c",
           infer=c(T,T),mode="latent",
           at=list(gndr.c=0,age10.c=0))

#effects for each DV-category
(mod3.antielite_salience.alt.eff<-
  contrast(mod3.antielite_salience.alt.trends,simple="DV.f",
         adjust="none","eff",infer=c(T,T)))

#save to file
export(data.frame(mod3.antielite_salience.alt.eff),
       "../../results/Added_covariates/mod3.antielite_salienceBYhealth.eff.MN.xlsx",
       overwrite=T)

#Use of conventional medicine

(mod3.antielite_salience.eff.CM<-
    contrast(mod3.antielite_salience.alt.trends,
         method = list("Conv - No conv" = contrast.weights.total(effects=mod3.antielite_salience.alt.eff,
                 signs=c(-2,-2,2,2))),
         simple="DV.f", infer=c(T,T)))

#Use of CAM

#weighted across all effects

(mod3.antielite_salience.eff.CAM<-
    contrast(mod3.antielite_salience.alt.trends,
         method = list("CAM - No CAM" = contrast.weights.total(effects=mod3.antielite_salience.alt.eff,
                 signs=c(-2,2,2,-2))),
         simple="DV.f", infer=c(T,T)))

# save to file
export(data.frame(rbind(
  mod3.antielite_salience.eff.CM,
  mod3.antielite_salience.eff.CAM,adjust="none")),
  "../../results/Added_covariates/mod3.antielite_salienceBYhealth.eff.COMB.xlsx")


```

### Probing simple slopes

```{r}
ref_grid(mod3.antielite_salience)

#pick points for inference

strain.on.health.c.points<-
  c(mean(fdat$strain.on.health.c)-
      sd(fdat$strain.on.health.c),
    mean(fdat$strain.on.health.c)-
      0*sd(fdat$strain.on.health.c),
    mean(fdat$strain.on.health.c)+
      sd(fdat$strain.on.health.c))

#conv

#low

mod3.antielite_salience.slopes.low<-
  emtrends(mod3.antielite_salience,~1|DV.f,
           var="antielite_salience.z",
           by="strain.on.health.c",
           at=list(strain.on.health.c=
                     strain.on.health.c.points[1],
                   gndr.c=0,
                   age.10.c=0),
           infer=c(T,T),
           mode="latent")

(mod3.antielite_salience.slopes.low.eff<-
  contrast(mod3.antielite_salience.slopes.low,
                                         simple="DV.f",
                                         adjust="none","eff",
           infer=c(T,T)))



#mid


mod3.antielite_salience.slopes.mid<-
  emtrends(mod3.antielite_salience,~1|DV.f,
           var="antielite_salience.z",
           by="strain.on.health.c",
           at=list(strain.on.health.c=
                     strain.on.health.c.points[2],
                   gndr.c=0,
                   age.10.c=0),
           infer=c(T,T),
           mode="latent")

(mod3.antielite_salience.slopes.mid.eff<-
  contrast(mod3.antielite_salience.slopes.mid,
                                         simple="DV.f",
                                         adjust="none","eff",
           infer=c(T,T)))


#high


mod3.antielite_salience.slopes.high<-
  emtrends(mod3.antielite_salience,~1|DV.f,
           var="antielite_salience.z",
           by="strain.on.health.c",
           at=list(strain.on.health.c=
                     strain.on.health.c.points[3],
                   gndr.c=0,
                   age.10.c=0),
           infer=c(T,T),
           mode="latent")

(mod3.antielite_salience.slopes.high.eff<-
  contrast(mod3.antielite_salience.slopes.high,
                                         simple="DV.f",
                                         adjust="none","eff",
           infer=c(T,T)))


# save to file

export(rbind(data.frame(mod3.antielite_salience.slopes.low.eff),
             data.frame(mod3.antielite_salience.slopes.mid.eff),
             data.frame(mod3.antielite_salience.slopes.high.eff)),
       "../../results/Added_covariates/mod3.antielite_salience.slopes.eff.MN.xlsx")


# combined CM for low

(mod3.antielite_salience.slopes.low.CM<-
  contrast(mod3.antielite_salience.slopes.low,
         method = list("Conv - No conv" = 
                         contrast.weights.total(
                           effects=
                           mod3.antielite_salience.slopes.low.eff,
                           signs=c(-2,-2,2,2))),
         simple="DV.f", infer=c(T,T)))


# combined CM for mid

(mod3.antielite_salience.slopes.mid.CM<-
  contrast(mod3.antielite_salience.slopes.mid,
         method = list("Conv - No conv" = 
                         contrast.weights.total(
                           effects=
                           mod3.antielite_salience.slopes.mid.eff,
                           signs=c(-2,-2,2,2))),
         simple="DV.f", infer=c(T,T)))


# combined CM for high

(mod3.antielite_salience.slopes.high.CM<-
  contrast(mod3.antielite_salience.slopes.high,
         method = list("Conv - No conv" = 
                         contrast.weights.total(
                           effects=
                           mod3.antielite_salience.slopes.high.eff,
                           signs=c(-2,-2,2,2))),
         simple="DV.f", infer=c(T,T)))



#Combined CAM for low


(mod3.antielite_salience.slopes.low.CAM<-
    contrast(mod3.antielite_salience.slopes.low,
         method = list("CAM - No CAM" = 
                         contrast.weights.total(
                           effects=
                           mod3.antielite_salience.slopes.low.eff,
                           signs=c(-2,2,2,-2))),
         simple="DV.f", infer=c(T,T)))


#Combined CAM for mid


(mod3.antielite_salience.slopes.mid.CAM<-
    contrast(mod3.antielite_salience.slopes.mid,
         method = list("CAM - No CAM" = 
                         contrast.weights.total(
                           effects=
                           mod3.antielite_salience.slopes.mid.eff,
                           signs=c(-2,2,2,-2))),
         simple="DV.f", infer=c(T,T)))

#Combined CAM for high


(mod3.antielite_salience.slopes.high.CAM<-
    contrast(mod3.antielite_salience.slopes.high,
         method = list("CAM - No CAM" = 
                         contrast.weights.total(
                           effects=
                           mod3.antielite_salience.slopes.high.eff,
                           signs=c(-2,2,2,-2))),
         simple="DV.f", infer=c(T,T)))

export(data.frame(rbind(
  mod3.antielite_salience.slopes.low.CM,
  mod3.antielite_salience.slopes.mid.CM,
  mod3.antielite_salience.slopes.high.CM,
  mod3.antielite_salience.slopes.low.CAM,
  mod3.antielite_salience.slopes.mid.CAM,
  mod3.antielite_salience.slopes.high.CAM,adjust="none")),
  "../../results/Added_covariates/mod3.antielite_salience.slopes.eff.COMB.xlsx")
```

## Model for corrupt_salience

```{r}
mod3.corrupt_salience<-
  mblogit(DV.f~gndr.c+age10.c+income.fr+
            edu.f+blgetmg.c+mstatus.c+strain.on.health.c+corrupt_salience.z+
            strain.on.health.c:corrupt_salience.z,
          random= ~1|cntry,
          estimator="ML",
          control = 
            mmclogit.control(maxit = 250,
                             trace=TRUE),
          data=fdat,weights=anweight)

anova(mod2.corrupt_salience,
      mod3.corrupt_salience,test="Chisq")

#Alternative model with manually defined interaction
fdat$corrupt_salience.zXstrain.on.health.c<-
  fdat$corrupt_salience.z*fdat$strain.on.health.c

mod3.corrupt_salience.alt<-
  mblogit(DV.f~gndr.c+age10.c+income.fr+
            edu.f+blgetmg.c+mstatus.c+strain.on.health.c+corrupt_salience.z+
            corrupt_salience.zXstrain.on.health.c,
          random= ~1|cntry,
          estimator="ML",
          control = 
            mmclogit.control(maxit = 250,
                             trace=TRUE),
          data=fdat,weights=anweight)


mod3.corrupt_salience.alt.trends<-
  emtrends(mod3.corrupt_salience.alt,~1|DV.f,
           var="corrupt_salience.zXstrain.on.health.c",
           infer=c(T,T),mode="latent",
           at=list(gndr.c=0,age10.c=0))

#effects for each DV-category
(mod3.corrupt_salience.alt.eff<-
  contrast(mod3.corrupt_salience.alt.trends,simple="DV.f",
         adjust="none","eff",infer=c(T,T)))

#save to file
export(data.frame(mod3.corrupt_salience.alt.eff),
       "../../results/Added_covariates/mod3.corrupt_salienceBYhealth.eff.MN.xlsx",
       overwrite=T)

#Use of conventional medicine

(mod3.corrupt_salience.eff.CM<-
    contrast(mod3.corrupt_salience.alt.trends,
         method = list("Conv - No conv" = contrast.weights.total(effects=mod3.corrupt_salience.alt.eff,
                 signs=c(-2,-2,2,2))),
         simple="DV.f", infer=c(T,T)))

#Use of CAM

#weighted across all effects

(mod3.corrupt_salience.eff.CAM<-
    contrast(mod3.corrupt_salience.alt.trends,
         method = list("CAM - No CAM" = contrast.weights.total(effects=mod3.corrupt_salience.alt.eff,
                 signs=c(-2,2,2,-2))),
         simple="DV.f", infer=c(T,T)))

# save to file
export(data.frame(rbind(
  mod3.corrupt_salience.eff.CM,
  mod3.corrupt_salience.eff.CAM,adjust="none")),
  "../../results/Added_covariates/mod3.corrupt_salienceBYhealth.eff.COMB.xlsx")


```

### Probing simple slopes

```{r}
ref_grid(mod3.corrupt_salience)

#pick points for inference

strain.on.health.c.points<-
  c(mean(fdat$strain.on.health.c)-
      sd(fdat$strain.on.health.c),
    mean(fdat$strain.on.health.c)-
      0*sd(fdat$strain.on.health.c),
    mean(fdat$strain.on.health.c)+
      sd(fdat$strain.on.health.c))

#conv

#low

mod3.corrupt_salience.slopes.low<-
  emtrends(mod3.corrupt_salience,~1|DV.f,
           var="corrupt_salience.z",
           by="strain.on.health.c",
           at=list(strain.on.health.c=
                     strain.on.health.c.points[1],
                   gndr.c=0,
                   age.10.c=0),
           infer=c(T,T),
           mode="latent")

(mod3.corrupt_salience.slopes.low.eff<-
  contrast(mod3.corrupt_salience.slopes.low,
                                         simple="DV.f",
                                         adjust="none","eff",
           infer=c(T,T)))



#mid


mod3.corrupt_salience.slopes.mid<-
  emtrends(mod3.corrupt_salience,~1|DV.f,
           var="corrupt_salience.z",
           by="strain.on.health.c",
           at=list(strain.on.health.c=
                     strain.on.health.c.points[2],
                   gndr.c=0,
                   age.10.c=0),
           infer=c(T,T),
           mode="latent")

(mod3.corrupt_salience.slopes.mid.eff<-
  contrast(mod3.corrupt_salience.slopes.mid,
                                         simple="DV.f",
                                         adjust="none","eff",
           infer=c(T,T)))


#high


mod3.corrupt_salience.slopes.high<-
  emtrends(mod3.corrupt_salience,~1|DV.f,
           var="corrupt_salience.z",
           by="strain.on.health.c",
           at=list(strain.on.health.c=
                     strain.on.health.c.points[3],
                   gndr.c=0,
                   age.10.c=0),
           infer=c(T,T),
           mode="latent")

(mod3.corrupt_salience.slopes.high.eff<-
  contrast(mod3.corrupt_salience.slopes.high,
                                         simple="DV.f",
                                         adjust="none","eff",
           infer=c(T,T)))


# save to file

export(rbind(data.frame(mod3.corrupt_salience.slopes.low.eff),
             data.frame(mod3.corrupt_salience.slopes.mid.eff),
             data.frame(mod3.corrupt_salience.slopes.high.eff)),
       "../../results/Added_covariates/mod3.corrupt_salience.slopes.eff.MN.xlsx")


# combined CM for low

(mod3.corrupt_salience.slopes.low.CM<-
  contrast(mod3.corrupt_salience.slopes.low,
         method = list("Conv - No conv" = 
                         contrast.weights.total(
                           effects=
                           mod3.corrupt_salience.slopes.low.eff,
                           signs=c(-2,-2,2,2))),
         simple="DV.f", infer=c(T,T)))


# combined CM for mid

(mod3.corrupt_salience.slopes.mid.CM<-
  contrast(mod3.corrupt_salience.slopes.mid,
         method = list("Conv - No conv" = 
                         contrast.weights.total(
                           effects=
                           mod3.corrupt_salience.slopes.mid.eff,
                           signs=c(-2,-2,2,2))),
         simple="DV.f", infer=c(T,T)))


# combined CM for high

(mod3.corrupt_salience.slopes.high.CM<-
  contrast(mod3.corrupt_salience.slopes.high,
         method = list("Conv - No conv" = 
                         contrast.weights.total(
                           effects=
                           mod3.corrupt_salience.slopes.high.eff,
                           signs=c(-2,-2,2,2))),
         simple="DV.f", infer=c(T,T)))



#Combined CAM for low


(mod3.corrupt_salience.slopes.low.CAM<-
    contrast(mod3.corrupt_salience.slopes.low,
         method = list("CAM - No CAM" = 
                         contrast.weights.total(
                           effects=
                           mod3.corrupt_salience.slopes.low.eff,
                           signs=c(-2,2,2,-2))),
         simple="DV.f", infer=c(T,T)))


#Combined CAM for mid


(mod3.corrupt_salience.slopes.mid.CAM<-
    contrast(mod3.corrupt_salience.slopes.mid,
         method = list("CAM - No CAM" = 
                         contrast.weights.total(
                           effects=
                           mod3.corrupt_salience.slopes.mid.eff,
                           signs=c(-2,2,2,-2))),
         simple="DV.f", infer=c(T,T)))

#Combined CAM for high


(mod3.corrupt_salience.slopes.high.CAM<-
    contrast(mod3.corrupt_salience.slopes.high,
         method = list("CAM - No CAM" = 
                         contrast.weights.total(
                           effects=
                           mod3.corrupt_salience.slopes.high.eff,
                           signs=c(-2,2,2,-2))),
         simple="DV.f", infer=c(T,T)))

export(data.frame(rbind(
  mod3.corrupt_salience.slopes.low.CM,
  mod3.corrupt_salience.slopes.mid.CM,
  mod3.corrupt_salience.slopes.high.CM,
  mod3.corrupt_salience.slopes.low.CAM,
  mod3.corrupt_salience.slopes.mid.CAM,
  mod3.corrupt_salience.slopes.high.CAM,adjust="none")),
  "../../results/Added_covariates/mod3.corrupt_salience.slopes.eff.COMB.xlsx")
```


# Exploratory analysis

## Nonlinearity

### lrgen

```{r}

fdat$lrgen.z.1<-fdat$lrgen.z
fdat$lrgen.z.2<-fdat$lrgen.z^2
fdat$lrgen.z.3<-fdat$lrgen.z^3

mod4.lrgen<-mblogit(DV.f~gndr.c+age10.c+income.fr+edu.f+blgetmg.c+mstatus.c+strain.on.health.c+
                       lrgen.z+I(lrgen.z^2)+I(lrgen.z^3),
                     random= ~1|cntry,
                     estimator="ML",
                     data=fdat,weights=anweight)

anova(mod2.lrgen,mod4.lrgen,test="Chisq")


```


### lrecon

```{r}

fdat$lrecon.z.1<-fdat$lrecon.z
fdat$lrecon.z.2<-fdat$lrecon.z^2
fdat$lrecon.z.3<-fdat$lrecon.z^3

mod4.lrecon<-mblogit(DV.f~gndr.c+age10.c+income.fr+edu.f+blgetmg.c+mstatus.c+strain.on.health.c+
                       lrecon.z+I(lrecon.z^2)+I(lrecon.z^3),
                     random= ~1|cntry,
                     estimator="ML",
                     data=fdat,weights=anweight)

anova(mod2.lrecon,mod4.lrecon,test="Chisq")


```



### galtan

```{r}

fdat$galtan.z.1<-fdat$galtan.z
fdat$galtan.z.2<-fdat$galtan.z^2
fdat$galtan.z.3<-fdat$galtan.z^3

mod4.galtan<-mblogit(DV.f~gndr.c+age10.c+income.fr+edu.f+
                       strain.on.health.c+
                       galtan.z+I(galtan.z^2)+I(galtan.z^3),
                     random= ~1|cntry,
                     estimator="ML",
                     data=fdat,weights=anweight)

anova(mod2.galtan,mod4.galtan,test="Chisq")

mod5.galtan<-mblogit(DV.f~gndr.c+age10.c+income.fr+edu.f+
                       strain.on.health.c+
                       galtan.z+I(galtan.z^2),
                     random= ~1|cntry,
                     estimator="ML",
                     data=fdat,weights=anweight)

anova(mod5.galtan,mod4.galtan,test="Chisq")


```


#### Simple slopes

```{r}

#low
mod4.galtan.slopes.low<-
  emtrends(mod4.galtan,~1|DV.f,
           var="galtan.z",
           by="galtan.z",
           at=list(strain.on.health.c=0,
                   gndr.c=0,
                   age10.c=0,
                   galtan.z=c(-1)),
           infer=c(T,T),
           mode="latent")


(mod4.galtan.slopes.low.eff<-
  contrast(mod4.galtan.slopes.low,
         simple="DV.f",
         infer=c(T,T),
         adjust="none","eff"))




#mid
mod4.galtan.slopes.mid<-
  emtrends(mod4.galtan,~1|DV.f,
           var="galtan.z",
           by="galtan.z",
           at=list(strain.on.health.c=0,
                   gndr.c=0,
                   age10.c=0,
                   galtan.z=c(0)),
           infer=c(T,T),
           mode="latent")


(mod4.galtan.slopes.mid.eff<-
  contrast(mod4.galtan.slopes.mid,
         simple="DV.f",
         infer=c(T,T),
         adjust="none","eff"))



#high
mod4.galtan.slopes.high<-
  emtrends(mod4.galtan,~1|DV.f,
           var="galtan.z",
           by="galtan.z",
           at=list(strain.on.health.c=0,
                   gndr.c=0,
                   age10.c=0,
                   galtan.z=c(1)),
           infer=c(T,T),
           mode="latent")


(mod4.galtan.slopes.high.eff<-
  contrast(mod4.galtan.slopes.high,
         simple="DV.f",
         infer=c(T,T),
         adjust="none","eff"))

#save to file

export(
  data.frame(
  rbind(
    mod4.galtan.slopes.low.eff,
    mod4.galtan.slopes.mid.eff,
    mod4.galtan.slopes.high.eff,adjust="none")),
  "../../results/Added_covariates/mod4.galtan.nonlinear.slopes.MN.xlsx")

# CM low

(mod4.galtan.slopes.low.eff.CM<-
    contrast(mod4.galtan.slopes.low,
         method = list("Conv - No conv" = 
                         contrast.weights.total(
                           effects=
                           mod4.galtan.slopes.low.eff,
                           signs=c(-2,-2,2,2))),
         simple="DV.f",infer=c(T,T)))

# CM mid

(mod4.galtan.slopes.mid.eff.CM<-
    contrast(mod4.galtan.slopes.mid,
         method = list("Conv - No conv" = 
                         contrast.weights.total(
                           effects=
                           mod4.galtan.slopes.mid.eff,
                           signs=c(-2,-2,2,2))),
         simple="DV.f",infer=c(T,T)))

# CM high

(mod4.galtan.slopes.high.eff.CM<-
    contrast(mod4.galtan.slopes.high,
         method = list("Conv - No conv" = 
                         contrast.weights.total(
                           effects=
                           mod4.galtan.slopes.high.eff,
                           signs=c(-2,-2,2,2))),
         simple="DV.f",infer=c(T,T)))



#CAM low

(mod4.galtan.slopes.low.eff.CAM<-
    contrast(mod4.galtan.slopes.low,
         method = list("CAM - No CAM" = 
                         contrast.weights.total(
                           effects=
                           mod4.galtan.slopes.low.eff,
                           signs=c(-2,2,2,-2))),
         simple="DV.f",infer=c(T,T)))

#CAM mid

(mod4.galtan.slopes.mid.eff.CAM<-
    contrast(mod4.galtan.slopes.mid,
         method = list("CAM - No CAM" = 
                         contrast.weights.total(
                           effects=
                           mod4.galtan.slopes.mid.eff,
                           signs=c(-2,2,2,-2))),
         simple="DV.f",infer=c(T,T)))

#CAM high

(mod4.galtan.slopes.high.eff.CAM<-
    contrast(mod4.galtan.slopes.high,
         method = list("CAM - No CAM" = 
                         contrast.weights.total(
                           effects=
                           mod4.galtan.slopes.high.eff,
                           signs=c(-2,2,2,-2))),
         simple="DV.f",infer=c(T,T)))


export(data.frame(rbind(mod4.galtan.slopes.low.eff.CM,
      mod4.galtan.slopes.mid.eff.CM,
      mod4.galtan.slopes.high.eff.CM,
      mod4.galtan.slopes.low.eff.CAM,
      mod4.galtan.slopes.mid.eff.CAM,
      mod4.galtan.slopes.high.eff.CAM,adjust="none")),
      "../../results/Added_covariates/mod4.galtan.nonlinear.slopes.COMB.xlsx")



```

### antielite_salience

```{r}

fdat$antielite_salience.z.1<-fdat$antielite_salience.z
fdat$antielite_salience.z.2<-fdat$antielite_salience.z^2
fdat$antielite_salience.z.3<-fdat$antielite_salience.z^3

mod4.antielite_salience<-
  mblogit(DV.f~gndr.c+age10.c+
            income.fr+edu.f+
            strain.on.health.c+
            antielite_salience.z+
            I(antielite_salience.z^2)+
            I(antielite_salience.z^3),
                     random= ~1|cntry,
                     estimator="ML",
                     data=fdat,weights=anweight)

anova(mod2.antielite_salience,
      mod4.antielite_salience,test="Chisq")


```



### corrupt_salience

```{r}

fdat$corrupt_salience.z.1<-fdat$corrupt_salience.z
fdat$corrupt_salience.z.2<-fdat$corrupt_salience.z^2
fdat$corrupt_salience.z.3<-fdat$corrupt_salience.z^3

mod4.corrupt_salience<-
  mblogit(DV.f~gndr.c+age10.c+
            income.fr+edu.f+blgetmg.c+mstatus.c+
            strain.on.health.c+
            corrupt_salience.z+
            I(corrupt_salience.z^2)+
            I(corrupt_salience.z^3),
                     random= ~1|cntry,
                     estimator="ML",
                     data=fdat,weights=anweight)

anova(mod2.corrupt_salience,
      mod4.corrupt_salience,test="Chisq")

```

# Print out custom functions

```{r,code=readLines("../custom_functions.R")}
```

# Session information

```{r}
s<-sessionInfo()
print(s,locale=F)
```